\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-16 manuscript/manuscript.tex
sp500

The KS statistic 
can be used to see if a population follows a hypothesized distribution and has 
and can be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
some of the common misuses of the one-sample KS test. One of the most common 
misuses of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where the data are serially
dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
semi-parametric
bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
where both the hypothesized 
distribution has unspecified parameters and the data are 
serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
this scenario also uses semi-parametric bootstrap.

@@

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the p-values do not appear to be 
completely aligned with the line
in the Q-Q plots for smaller sample sizes like $n = 100$ or $200$, they match
the lines very closely for $n = 1600$ and $3200$. More importantly, almost
all of the p-values appear to be within the confidence bands when looking at the
plots zoomed in to probabilities between 0 and 0.1 in 
Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}, and as stated 
before, 
researchers are unlikely to choose significance levels above 0.1.

>>>>

The KS statistic 
can be used to see if a population follows a hypothesized distribution and can 
be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
some of the common misuses of the one-sample KS test. One of the most common 
misuses of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where the data are serially
dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
semi-parametric
bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
where both the hypothesized 
distribution has unspecified parameters and the data are 
serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
this scenario also uses semi-parametric bootstrap.

@@

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
although the extent to which the p-values appear to be 
completely aligned with the line
in the Q-Q plots is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in the Q-Q plots, even
in Figures~\ref{fig:zoom_normal} and \ref{fig:zoom_gamma}. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high. Additionally, performance generally seems
better for negative $\tau$ values versus positive $\tau$ values of the same
strength.
